The Rapid Cycleway Prioritisation Tool

### 2020-06-15 rapid-slides.Rmd
Update slides

@@

@@

>>>>

```{r, include=FALSE}
library(dplyr)
```

@@

background-image: url(https://pbs.twimg.com/media/EZvQNJlWoAE4D_c?format=jpg&name=4096x4096)

@@

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

1) reduced capacity on public transport 2) need for space so physical distancing guidelines can be followed
3) healthy restart 4) need to act fast

### How to cope with reduced public transport capacity post COVID-19?

Plans from Leeds City Council responding to national [guidance](https://www.gov.uk/government/publications/reallocating-road-space-in-response-to-covid-19-statutory-guidance-for-local-authorities) and [funding](https://www.gov.uk/government/news/2-billion-package-to-create-new-era-for-cycling-and-walking) for 'pop-up' cycleways:

![](https://pbs.twimg.com/media/EZ_-A0dXgAAlBzt?format=png&name=900x900)

## Spatial networks can support planning

### Transport networks are spatial networks

Spatial network representation in R:

![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/mapout.png)

background-image: url("https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/facet-output.png")
background-position: right
background-size: contain

### sf + igraph used in project to support investment in 'pop-ups' nationwide

Every city in England

Results in Leeds:

```{r, echo=FALSE, results='markup'}
res_leeds = sf::read_sf("https://www.cyipt.bike/rapid/west-yorkshire/top_routes.geojson")
res_leeds %>% 
  arrange(desc(mean_cycling_potential)) %>% 
  slice(1:5) %>%
  sf::st_drop_geometry() %>% 
  dplyr::select(name) %>% 
  as.data.frame()
```

Cycleway planned for

Kirkstall Road (source: [BBC](https://www.bbc.co.uk/news/uk-england-leeds-52577554))

Free and open results:

[www.cyipt.bike/rapid](https://www.cyipt.bike/rapid)

Source code: [github.com/cyipt/popupCycleways](https://github.com/cyipt/popupCycleways)

<!-- ![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/facet-output.png) -->

```{r, out.width="70%", echo=FALSE}
# knitr::include_graphics("https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/facet-output.png")
```

## Ingredients to prioritise transport infrastructure

.left-column[

- Current travel patterns
- Road attribute data 
- Potential usage levels
- Impact on overall network

**Spatial networks can help, especially with the last two**

Source: https://www.pct.bike/

]

.right-column[

![](figs/pct.png)

]
